```{r}
library(httpgd)
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(cowplot)
library(ktools)
library(hrbrthemes)
library(inlmisc)
options(ggplot2.discrete.fill=unname(inlmisc::GetColors(9, scheme = "muted")), 
        ggplot2.discrete.colour=unname(inlmisc::GetColors(9, scheme = "muted")))
library(survey)
library(rdhs)

options(ggplot2.discrete.colour = hcl.colors(8))
set.seed(111)

library(tagger)

theme = theme(strip.background = element_rect(fill='grey95', color = 'grey70', size = .3), 
							panel.border = element_rect(color = 'grey70'))
```

# Show biases asumptions

```{r}
# Biases forms
bias_lgt = function(age, mid=23, maxx=4.5, r=.4) {
	maxx / (1 + exp(-r * (age - mid))) - 2
}


tibble(age = 15:55) |> 
	mutate(`Bias type I` =  .5 + bias_lgt(age, r = .25) + rnorm(n(), 0, .3)) |> 
	mutate(`Bias type II` =  .5 - bias_lgt(age,,2.5) + rnorm(n(), 0, .3)) |> 
  pivot_longer(-age, names_to = 'type', values_to = "bias") |>
	ggplot() + 
    geom_line(aes(age, bias)) + labs(x='Age at interview', y='Bias') +
    facet_wrap(~type, 2) + 
    tag_facets(tag_pool = char(A.1, B.1)) +
    the_theme -> b

yoblab = seq(1970, 1999, 5) %>% paste(.+4, sep="-") %>% magrittr::extract(1:5)

# Resulting survey data
biases_data = 
	tibble(yob = 1970:2020, afs = 17) %>% 
	uncount(4, .id = 'sv') %>% mutate(sv = 2000 + (sv-1)*5) %>% 
	mutate(
    aar = sv - yob, 
    include = aar >=15) %>% 
  filter(include) %>% 
	mutate(
    bias_women = .5-bias_lgt(aar,,2.5) + rnorm(n(), 0, .3),
    bias_men =  .5+bias_lgt(aar, r=.25) + rnorm(n(), 0, .3),
    yobgr = findInterval(yob, seq(1970, 1999, 5))) %>% 
	pivot_longer(bias_women:bias_men, names_prefix='bias_', names_to='type', values_to='bias') %>% 
	group_by(sv, yobgr, type) %>% 
	summarise(afs = median(afs + bias)) %>% 
	filter(yobgr != 6) %>%
	group_by(type, yobgr) %>% 
	mutate(
    note = if_else(sv == min(sv), yoblab[yobgr], NA_character_),
    type = if_else(type == 'men', 'Bias type I', 'Bias type II'),
    sv = paste("Survey", sv)
    )

biases_data |> 
	ggplot() +
  geom_hline(yintercept=17, color = 'dimgrey', linetype = 'dashed') +
  geom_col(
    aes(factor(yobgr, labels = yoblab), afs), 
    fill='#FCF4DC', color = '#A57706', size=.3, 
    position = position_dodge2(, "single")) +
  geom_text(aes(yobgr, 7, label = sv), color = '#0A2933', 
    angle = 90, position = position_dodge2(.9,"single")) +
	facet_wrap(~type, 2) +
  tag_facets(tag_pool = char(A.2, B.2)) +
	coord_cartesian(expand = .1) +
	labs(x = "Birth cohort", y = "Median AFS") + 
  the_theme -> g

ggarrange(b, g, ncol=2, widths = c(.3, .7))
hgd_plot(width = 700, height = 500, renderer = "pdf", file = "Bias_type.pdf")

# show cases of within-cohort inconsistency

## Pull with `rdhs`

```{r}
# SSA = fread('data/SSA_AFS.csv.bz2') %>% filter(ver == "DHS"
rdhs::set_rdhs_config(email = "ath19@ic.ac.uk", 
                      project = "Statistics and Machine Learning for HIV")

debugonce(dhs_datasets)

datasets <- dhs_datasets(char(SN, ET, GN, ZM), 
                         fileFormat = "flat", 
                         fileType = c("MR", "IR"))

datasets %<>% 
  filter(SurveyYear >= 1996) %>% 
  mutate(sex = if_else(FileType == "Individual Recode", "female", "male"))

downloads <- get_datasets(datasets$FileName)
names(downloads)

# it seems that this fixes it
# 
# add a check for "not authorized for this country." error in
# response = httr::GET() from get_datasets
# httr::content(response, "text")
# 
# rdhs:::.rdhs$client$get_datasets(dataset_filenames = "SNMR31FL.ZIP")
# rdhs:::.rdhs$client$available_datasets()
```
## Extract AFS

```{r}
search_variable_labels(datasets$FileName, "age at first sex")

get_afs <- function(x) {
  o <- readRDS(downloads[[x]]) %>% 
    as_tibble %>% 
    mutate(lab = datasets$SurveyId[x])
  if (datasets$sex[x]=="male") {
    if (exists("mv531", where = o))
      o <- o %>% 
        dplyr::select(psu = mv021, strata = mv023, weights = mv005,
               dob = mv011, doi = mv008, afs = mv531, lab)
    else if (exists("mv525", where = o))
      o <- o %>% 
        dplyr::select(psu = mv021, strata = mv023, weights = mv005,
               dob = mv011, doi = mv008, afs = mv525, lab)
    else
      return(NULL)
  } else {
    if (exists("v531", where = o))
      o <- o %>% 
        dplyr::select(psu = v021, strata = v023, weights = v005,
               dob = v011, doi = v008, afs = v531, lab)
    else if (exists("v525", where = o))
      o <- o %>% 
        dplyr::select(psu = v021, strata = v023, weights = v005,
               dob = v011, doi = v008, afs = v525, lab)
    else
      return(NULL)
  }
  o %>%
    mutate(iso = substr(lab, 1, 2),
           dob = if_else(iso == "ET", dob + 92L, dob),
           doi = if_else(iso == "ET", doi + 92L, doi),
           yob = cmc_to_year(dob), svy = cmc_to_year(doi), 
           age = svy - yob, sex = datasets$sex[x]) %>% 
    drop_na() 
}

dta <- lapply(seq_along(downloads), get_afs)

labs = paste( seq(1970, 1999, 5), seq(1970, 1999, 5) + 4, sep = "-" )

dtab <- bind_rows(dta) %>% 
  filter(yob >= 1970 & yob < 2000) %>%
  mutate(yobgrp = findInterval(yob, seq(1970, 2000, 5)),
         yobgrp = factor(yobgrp, labels = labs)) %>%
  filter(afs <= 55 & age >= 18 & yob < 1990) %>% 
  mutate(event = afs != 0, ever18 = as.integer(event & afs < 18))
dtab
```

## Survey designs and stats

```{r}
design <- svydesign(id=dtab$psu, 
                    strata=dtab$strata, 
                    weights=dtab$weights, data=dtab, nest = TRUE)

afsby <- svyby(formula = ~ever18, 
               by = ~lab + yobgrp + sex, 
               design = design, 
               FUN = svyciprop, 
               vartype = "ci")
	
plot_data <- afsby %>%
  mutate(svy = substr(lab, 3, 6), iso = substr(lab, 1, 2)) %>% 
  filter(!(iso == "ET" & sex == "male")) %>% 
  filter(!(iso == "GN" & sex == "female")) %>% 
  filter(!(iso == "SN" & sex == "male")) %>% 
  filter(!(iso == "ZM" & sex == "female")) %>% 
  # restrict the number of consecutive surveys in Senegal
  filter(!(iso == "SN" & svy %in% c(2014:2018))) %>% 
  filter(!(iso == "ZM" & svy %in% c(1996))) %>% 
  mutate(sex = tools::toTitleCase(sex), ISO_A3 = iso2name(iso), 
         lab = paste0("DHS", svy),
         grp = interaction(sex, ISO_A3, sep=" - "),
         grp = factor(grp, levels = c("Male - Guinea", 
		                                  "Male - Zambia", 
		                                  "Female - Ethiopia", 
		                                  "Female - Senegal")))
  
plot_data |>
mutate(
  svy = as.numeric(svy),
  aar = paste0(
    svy - as.numeric(substr(yobgrp, 6, 9)), 
    "-",
    svy - as.numeric(substr(yobgrp, 1, 4))),
  lab = paste0(lab, "\n", bracket(aar))) |> 
  ggplot() +
		geom_col(
		  aes(yobgrp, ever18), 
		  fill='#FCF4DC', color = '#A57706', size=.3, 
		  position = position_dodge2(, "single")) +
    geom_linerange(
      aes(yobgrp, ever18, ymin = ci_l, ymax = ci_u),
      position = position_dodge2(.9, "single"), size = 1.2, color = "#A57706") +
		geom_text(aes(yobgrp, 0.08, label = lab), color = '#0A2933', size = 2.3, 
		          angle = 90, position = position_dodge2(.9,"single")) +
		facet_grid(rows = vars(grp), space="free", scales="free") +
		labs(x = "Birth cohort", y = "", fill = "Survey year", 
				 title = "Percentage ever had sex under 18 by survey years", 
				 subtitle = "among 18+ year-old respondents",
				 linetype = 'Birth cohort', color = 'Birth cohort') +
		coord_cartesian(expand = .1) +
		scale_y_continuous(labels=scales::percent) + 
		theme_bw() +
        theme(legend.position = "none", 
              strip.background = element_rect(fill='grey95', color = 'grey70', size = .3), 
              panel.border = element_rect(color = 'grey70'),
              axis.text.x = element_text(angle = 0, size = 9)) -> g
g
quartz_off(g, 'data_discrepancy', 7, 7, open=1)
```